Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-04 WSSSPE1_report/WSSSPE1_summary_report.tex
flag about sustainability discussion
List of Attendees Appendix: removing twitter/email/affil info

@@

What is sustainable? What are the best practices, can workshops fund meetings to help define and improve best practices in these areas? Software plans from the funding agencies? \todo{mention as cross-cutting, since this came up in other parts of the workshop as well?}

@@

Daniel S. Katz (@danielskatz)

Neil Chue Hong (@npch)

Gabrielle Allen

David Proctor (@djproctor)

Manish Parashar

Jay Alameda (alameda@illinois.edu)

David Andrs

Lorena A Barba (@LorenaABarba)

David Bernholdt (bernholdtde@ornl.gov)

Phil Bourne

Karl Broman (@kwbroman)

Maxine Brown, UIC (maxine@uic.edu)

David Bruhwiler   (bruhwiler@radiasoft.net    @radiasoft)

Bruno Bzeznik

Jeffrey Carver, University of Alabama (carver@cs.ua.edu)

John W. Cobb (cobbjw@ornl.gov, @johnwcobb)

Karen Cranston (@kcranstn, National Evolutionary Synthesis Center)

Rion Dooley

Anshu Dubey (adubey@lbl.gov)

Ian Foster, @ianfoster

Juliana Freire

Derek Gaston

Derek Groen (@whydoitweet on Twitter)

Edmund Hart (@distribecology)

James Hetherington @jamespjh

Simon Hettrick (s.hettrick@software.ac.uk)

Kenneth Hoste (@kehoste, Ghent University, Belgium)

James Howison, University of Texas at Austin (@jameshowison)

Daisie Huang

Kerk Kee (kerk.kee@gmail.com)

Arnaud Legrand

Paul Madden, NOAA / University of Colorado, maddenp@colorado.edu

Louis Maddox (@lmmddx)

Ketan Maheshwari (@km\_9 on Twitter)

Suresh Marru (smarru@iu.edu, @sureshmarru)

Cezary Mazurek, mazurek@man.poznan.pl, @cezary\_mazurek

James McClure

Chris Mentzel @chrismentzel - firstname dot lastname at moore dot org

J. Yates Monteith, Clemson University

Pierre Neyron

Lucas Nussbaum (lucas.nussbaum@loria.fr)

Cody Permann

John Peterson

Quan Pham, University of Chicago

Marlon Pierce, marpierc@iu.edu, @marpierc

Heather Piwowar

Jason Riedy, Georgia Tech, http://fmrl.me/jasonriedy and many other places

Andreas Schreiber (@onyame)

William Scullin

Andrew Slaughter

Arfon Smith

James Spencer (@exp\_n)

Shel Swenson, University of Southern California (shel.swenson@usc.edu)

Fr\'{e}d\'{e}ric Suter

Andy Terrel (@aterrel, andy.terrel@gmail.com, NumFOCUS and Continuum Analytics)

George K. Thiruvathukal, Loyola University Chicago and Computing in Science and Engineering (IEEE CS/AIP) (gkt@cs.luc.edu)

John Towns

Erik Trainer

Matthew Turk (@powersoffour on Twitter, matthewturk@gmail.com)

Eric Van Wyk, University of Minnesota, evw@cs.umn.edu, @ericvanwyk

Colin C. Venters, c.venters@hud.ac.uk

Von Welch, @VonWelch

Nancy Wilkins-Diehr, wilkinsn@sdsc.edu

Theresa Windus (twindus@iastate.edu)

Rich Wolski

Lynn Zentner

Frank Löffler

Patrick O'Leary

>>>>

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

@@

What is sustainable? What are the best practices, can workshops fund meetings to help define and improve best practices in these areas? Software plans from the funding agencies? This topic is expanded upon in \S\ref{sec:cross-cutting}, since it was discussed up in multiple parts of the WSSSPE1 workshop.

@@

\begin{tabular}{ L{4cm}  L{4cm}  L{4cm}  L{4cm} }
   Daniel S. Katz
&  Neil Chue Hong
&  Gabrielle Allen
&  David Proctor
\\ Manish Parashar
&  Jay Alameda
&  David Andrs
&  Lorena A Barba
\\ David Bernholdt
&  Phil Bourne
&  Karl Broman
&  Maxine Brown
\\ David Bruhwiler
&  Bruno Bzeznik
&  Jeffrey Carver
&  John W. Cobb
\\ Karen Cranston
&  Rion Dooley
&  Anshu Dubey
&  Ian Foster
\\Juliana Freire
& Derek Gaston
& Derek Groen
& Edmund Hart
\\James Hetherington
& Simon Hettrick
& Kenneth Hoste
& James Howison
\\Daisie Huang
& Kerk Kee
& Arnaud Legrand
& Paul Madden
\\Louis Maddox
& Ketan Maheshwari
& Suresh Marru
& Cezary Mazurek
\\James McClure
& Chris Mentzel
& J. Yates Monteith
& Pierre Neyron
\\Lucas Nussbaum
& Cody Permann
& John Peterson
& Quan Pham
\\Marlon Pierce
& Heather Piwowar
& Jason Riedy
& Andreas Schreiber
\\William Scullin
& Andrew Slaughter
& Arfon Smith
& James Spencer
\\Shel Swenson
& Fr\'{e}d\'{e}ric Suter
& Andy Terrel
& George  Thiruvathukal
\\John Towns
& Erik Trainer
& Matthew Turk
& Eric Van Wyk
\\Colin C. Venters
& Von Welch
& Nancy Wilkins-Diehr
& Theresa Windus
\\Rich Wolski
& Lynn Zentner
& Frank Löffler
& Patrick O'Leary
\end{tabular}
